Identifying Departures from the Fully Developed Speckle Hypothesis in Intensity SAR Data with Non-Parametric Estimation of the Entropy

### 2024-01-17 Text/Articles/MIGARS_2024/R1-The Entropy as a Proxy for Fully Developed Speckle.Rmd
add coefficient of variation (CV)

R <- 1000
mu <- 1
B <- 2
alpha1 <- -8
sample.size <- c(50, 100, 150, 200, 250,300, 350)
L_values <- c(2, 5, 8, 18)

@@

# For each L
for (L in L_values) {
  TestStatistics1 <- list()  
  summary_stats <- data.frame( LValue = character(),
                              SampleSize = numeric(),
                              Mean = numeric(),
                              SD = numeric(),
                              Variance = numeric(),
                              Skewness = numeric(),
                              Kurtosis = numeric(),
                              adpvalue = numeric()
                              )  # Nueva columna para  L
  # summary_normality <- data.frame(Sample_Size = numeric(),
  #                               lillie_p_value = numeric(),
  #                               ad_p_value = numeric())
  #normality_test <- list()#

@@

    mean_val <- mean(TestStat1)
    sd_val <- sd(TestStat1)
    var_val <- var(TestStat1)
    skewness_val <- skewness(TestStat1)
    kurtosis_val <- kurtosis(TestStat1)
   # lillie_p_value <- lillie.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
    ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value

    summary_stats <- rbind(summary_stats, data.frame(LValue = as.character(L),
                                                     SampleSize = s,
                                                     Mean = mean_val,
                                                     SD = sd_val,
                                                     Variance = var_val,
                                                     Skewness = skewness_val,
                                                     Kurtosis = kurtosis_val,
                                                     adpvalue = ad_p_value
                                                     ))

@@

)
colnames(combined_summary_stats) <- c("$L$", "$n$", "Mean", "SD", "Var", "Skewness", "Kurtosis", "$p$-value")

>>>>

R <- 500
mu <- 1
B <- 2
alpha1 <- -8
sample.size <- c(50, 100, 150, 200, 250,300, 350)
L_values <- c(2, 5, 8, 18)

@@

# For each L
for (L in L_values) {
  TestStatistics1 <- list()  
  summary_stats <- data.frame( LValue = character(),
                              SampleSize = numeric(),
                              Mean = numeric(),
                              SD = numeric(),
                              Variance = numeric(),
                              CV= numeric(),
                              Skewness = numeric(),
                              Kurtosis = numeric(),
                              adpvalue = numeric()
                              )  # Nueva columna para  L
  # summary_normality <- data.frame(Sample_Size = numeric(),
  #                               lillie_p_value = numeric(),
  #                               ad_p_value = numeric())
  #normality_test <- list()#

@@

    mean_val <- mean(TestStat1)
    sd_val <- sd(TestStat1)
    var_val <- var(TestStat1)
    skewness_val <- skewness(TestStat1)
    kurtosis_val <- kurtosis(TestStat1)
   # lillie_p_value <- lillie.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
    ad_p_value <- ad.test(TestStatistics1[[as.character(s)]]$Test_Statistics)$p.value
    cv_val <- (sd_val / mean_val)

    summary_stats <- rbind(summary_stats, data.frame(LValue = as.character(L),
                                                     SampleSize = s,
                                                     Mean = mean_val,
                                                     SD = sd_val,
                                                     Variance = var_val,
                                                      CV = cv_val,
                                                     Skewness = skewness_val,
                                                     Kurtosis = kurtosis_val,
                                                     adpvalue = ad_p_value
                                                     ))

@@

)
colnames(combined_summary_stats) <- c("$L$", "$n$", "Mean", "SD", "Var", "CV", "Skewness", "Kurtosis", "$p$-value")
